Scheduling and Vectorization for MPC

### 2022-02-28 paper_SIMD.tex
Minor formatting.

\begin{verbatim}
for i in range(N):
  A[i] = B[i] + 10;
  B[i] = A[i] * D[i-1];
  C[i] = A[i] * D[i-1];
  D[i] = B[i] * C[i];
\end{verbatim}

@@

\begin{verbatim}
for i in range(N):
1. A_1 = PHI(A_0,A_2)
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. A_2 = update(A_1, i, B_1[i] + 10); 
6. B_2 = update(B_1, i, A_2[i] * D_1[i-1]);
7. C_2 = update(C_1, i, A_2[i] * D_1[i-1]);
8. D_2 = update(D_1, i, B_2[i] * C_2[i]);
\end{verbatim}

@@

\begin{verbatim}
for i in range(N):
1. A_1 = PHI(A_0,A_2)
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. A_2 = update(A_1, I, B_1[I] + 10); 
6. B_2 = update(B_1, I, A_2[I] * D_1[I-1]);
7. C_2 = update(C_1, I, A_2[I] * D_1[I-1]);
8. D_2 = update(D_1, I, B_2[I] * C_2[I]);
\end{verbatim}

@@

\begin{verbatim}
1. A_2 = update(A_0, I, ADD_SIMD(B_0[I],10));
   equiv. to A_2[I] = ADD_SIMD(B_0[I],10)
FOR i=0; i<N; i++; // MOTION loop
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. B_2 = update(B_1, i, A_2[i] * D_1[i-1]);
   equiv. to B_2 = B_1; B_2[i] = A_2[i] * D_1[i-1];
6. C_2 = update(C_1, i, A_2[i] * D_1[i-1]);
7. D_2 = update(D_1, i, B_2[i] * C_2[i]);
\end{verbatim}

@@

\begin{verbatim}
for i in range(0, num_bins):
   res1 = PHI(res, res2)
   for j in range(0, N):
      res2 = PHI(res1, res3)
      tmp1 = (A[j] == i)
      tmp2 = (res2[i] + B[j])
      tmp3 = MUX(tmp1, res2[i], tmp2)
      res3 = Update(res2, i, tmp3)     
return res1
\end{verbatim}

@@

\begin{verbatim}
A1 = raise_dim(A, j, ((i:num_bins),(j:N)))
B1 = raise_dim(B, j, ((i:num_bins),(j:N)))
I = raise_dim(i, ((i:num_bins),(j:N)))
for i in range(0, num_bins):
   res1 = PHI(res, res2) // target-less, no drop_dim
   res1' = raise_dim(res1, (j:N))
   for j in range(0, N):
      res2 = PHI(res1', res3)
      tmp1 = (A1 == I)
      tmp2 = (res2 + B1)
      tmp3 = MUX(tmp1, res2, tmp2)
      res3 = res2 // copy propagation: res2 into res3
      res3 = tmp3 // "normal": res3[I,J] = tmp3[I,J]    
return res1
\end{verbatim}

@@

\begin{verbatim}
A1 = raise_dim(A, j, ((i:num_bins),(j:N)))
B1 = raise_dim(B, j, ((i:num_bins),(j:N)))
I1 = raise_dim(i, ((i:num_bins),(j:N)))

@@

res1' = raise_dim(res, (j:N)) // raising original array to a 2-dimensional array
for j in range(0, N):
   res2 = PHI(res1', res3)
   tmp2[I,j] = (res2[I,j] + B1[I,j])
   tmp3[I,j] = MUX(tmp1[I,j], res2[I,j], tmp2[I,j])
   res3 = res2
   res3[I,j] = tmp3[I,j]
res1 = drop_dim(res2) // Have to add drop_dim before removing redundant phi-node      
return res1
\end{verbatim}

@@

for j in range(0, N):
   res2 = PHI(res1', res3) // now 1-dim array
   tmp2[I] = (res2[I] + B1[I,j])
   tmp3[I] = MUX(tmp1[I,j], res2[I], tmp2[I])
   res3 = res2
   res3[I] = tmp3[I]
return res2
\end{verbatim}

>>>>

{\small
\begin{verbatim}
for i in range(N):
  A[i] = B[i] + 10;
  B[i] = A[i] * D[i-1];
  C[i] = A[i] * D[i-1];
  D[i] = B[i] * C[i];
\end{verbatim}
}

@@

{\small
\begin{verbatim}
for i in range(N):
1. A_1 = PHI(A_0,A_2)
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. A_2 = update(A_1, i, B_1[i] + 10); 
6. B_2 = update(B_1, i, A_2[i] * D_1[i-1]);
7. C_2 = update(C_1, i, A_2[i] * D_1[i-1]);
8. D_2 = update(D_1, i, B_2[i] * C_2[i]);
\end{verbatim}
}

@@

{\small
\begin{verbatim}
for i in range(N):
1. A_1 = PHI(A_0,A_2)
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. A_2 = update(A_1, I, B_1[I] + 10); 
6. B_2 = update(B_1, I, A_2[I] * D_1[I-1]);
7. C_2 = update(C_1, I, A_2[I] * D_1[I-1]);
8. D_2 = update(D_1, I, B_2[I] * C_2[I]);
\end{verbatim}
}

@@

{\small
\begin{verbatim}
1. A_2 = update(A_0, I, ADD_SIMD(B_0[I],10));
   equiv. to A_2[I] = ADD_SIMD(B_0[I],10)
FOR i=0; i<N; i++; // MOTION loop
2. B_1 = PHI(B_0,B_2)
3. C_1 = PHI(C_0,C_2)
4. D_1 = PHI(D_0,D_2)
5. B_2 = update(B_1, i, A_2[i] * D_1[i-1]);
   equiv. to B_2 = B_1; B_2[i] = A_2[i] * D_1[i-1];
6. C_2 = update(C_1, i, A_2[i] * D_1[i-1]);
7. D_2 = update(D_1, i, B_2[i] * C_2[i]);
\end{verbatim}
}

@@

{\small
\begin{verbatim}
for i in range(0, num_bins):
   res1 = PHI(res, res2)
   for j in range(0, N):
      res2 = PHI(res1, res3)
      tmp1 = (A[j] == i)
      tmp2 = (res2[i] + B[j])
      tmp3 = MUX(tmp1, res2[i], tmp2)
      res3 = Update(res2, i, tmp3)     
return res1
\end{verbatim}
}

@@

{\small
\begin{verbatim}
A1 = raise_dim(A, j, ((i:num_bins),(j:N)))
B1 = raise_dim(B, j, ((i:num_bins),(j:N)))
I = raise_dim(i, ((i:num_bins),(j:N)))
for i in range(0, num_bins):
   res1 = PHI(res, res2) // target-less, no drop_dim
   res1' = raise_dim(res1, (j:N))
   for j in range(0, N):
      res2 = PHI(res1', res3)
      tmp1 = (A1 == I)
      tmp2 = (res2 + B1)
      tmp3 = MUX(tmp1, res2, tmp2)
      res3 = res2 // copy propagation: res2 into res3
      res3 = tmp3 // "normal": res3[I,J] = tmp3[I,J]    
return res1
\end{verbatim}
}

@@

{\small
\begin{verbatim}
A1 = raise_dim(A, j, ((i:num_bins),(j:N)))
B1 = raise_dim(B, j, ((i:num_bins),(j:N)))
I1 = raise_dim(i, ((i:num_bins),(j:N)))

@@

res1' = raise_dim(res, (j:N)) // raising res to a 2-dim. array
for j in range(0, N):
   res2 = PHI(res1', res3)
   tmp2[I,j] = (res2[I,j] + B1[I,j])
   tmp3[I,j] = MUX(tmp1[I,j], res2[I,j], tmp2[I,j])
   res3 = res2
   res3[I,j] = tmp3[I,j]
res1 = drop_dim(res2) // Have to add drop_dim before removing redundant phi-node      
return res1
\end{verbatim}
}

@@

for j in range(0, N):
   res2 = PHI(res1', res3) // now 1-dim array
   tmp2[I] = (res2[I] + B1[I,j])
   tmp3[I] = MUX(tmp1[I,j], res2[I], tmp2[I])
   res3 = res2
   res3[I] = tmp3[I]
return res2
\end{verbatim}
}
